A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2023-07-13 kobakian-cook.Rmd
Load data

# Contiguous Cartograms
if (!file.exists("data/ncont.rda")) {
  cont <- sa2thyroid_ERP %>% 
    mutate(Population = Population + 1) %>% 
    cartogram_cont(., weight = "Population", itermax = 20) %>%
    st_as_sf()
  save(cont, file = "data/cont.rda") 
}

>>>>

# Contiguous Cartograms
if (!file.exists("data/cont.rda")) {
  cont <- sa2thyroid_ERP %>% 
    mutate(Population = Population + 1) %>% 
    cartogram_cont(., weight = "Population", itermax = 20) %>%
    st_as_sf()
  save(cont, file = "data/cont.rda") 
}
